Improving cropland maps through tight integration of human and machine intelligence

### 2019-06-17 manuscript/manuscript.Rmd
More paragraphs added to introduction

These problems arising from cropland characteristics are increasingly being overcome due to technological advances. Recent advances in satellite technology have increased the coverage of high (<5 m) or near-high (10 m) resolution imagery with weekly to near-daily return intervals [@DruschSentinel2ESAOptical2012; @McCabefutureEarthobservation2017]. This spatial and temporal resolution addresses the sensor-scale mismatch, and can capture the intra-seasonal dynamics of cropland more effectively, which helps classifiers more effectively distinguish cropland from surrounding cover types [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. On top of this, advances in cloud computing [@GorelickGoogleEarthEngine2017a], the opening of extensive image archives [@WulderglobalLandsatarchive2016], and next generation machine learning approaches [@MaxwellImplementationmachinelearningclassification2018; @ZhuDeeplearningremote2017] are being leveraged to create improved and higher resolution (20-30 m) of cropland and landcover for Africa and globally [@ChenGloballandcover2015; @ESACCILAND; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017]

>>>>

These problems arising from cropland characteristics are increasingly being overcome due to technological advances. Recent advances in satellite technology have increased the coverage of high (<5 m) or near-high (10 m) resolution imagery with weekly to near-daily return intervals [@DruschSentinel2ESAOptical2012; @McCabefutureEarthobservation2017]. This spatial and temporal resolution addresses the sensor-scale mismatch, and more effectively captures the intra-seasonal dynamics of cropland, which helps classifiers distinguish cropland from surrounding cover types [@Debatsgeneralizedcomputervision2016; @Defournyrealtimeagriculturemonitoring2019]. On top of this, advances in cloud computing [@GorelickGoogleEarthEngine2017a], the opening of image archives [@WulderglobalLandsatarchive2016], and next generation machine learning approaches [@MaxwellImplementationmachinelearningclassification2018; @ZhuDeeplearningremote2017] are placing large volumes of these moderate to near-high resolution imagery together with the computational and algorithmic resources necessary to classify them at scale. These capabilities are aleady being used to create a new generation of higher resolution (20-30 m) cropland and landcover maps for Africa and other regions [@ChenGloballandcover2015; @ESAESACCILAND; @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017].

Despite these advances, the highest resolution (<5 m) image sources are still not used to map cropland over large extents because they are commercial and relatively high cost to acquire. As such, map accuracy still remains below desired levels, as many of these newer maps still have accuracies in the 60-75% range for the cropland class [e.g. @LesivEvaluationESACCI2017; @XiongNominal30mCropland2017]. Accuracy may also be compromised because of factors that are new or becoming more pronounced as a consequence of the recent technological gains, particularly with respect to new algorithms and the manner in which these are trained. Advances in machine learning are helping to greatly improve classification skill, but these algorithms generally require large training datasets [@MaxwellImplementationmachinelearningclassification2018], particularly neural network-based "deep-learning" methods (cite). To satisfy this need for more training samples, map-makers increasingly rely on visual interpretation of high resolution satellite or aerial imagery to collect training (or validation) samples [e.g. @XiongNominal30mCropland2017; @ChenGloballandcover2015]. Several platforms have been developed to facilitate such efforts [e.g. @BeyCollectEarthLand2016; @Estesplatformcrowdsourcingcreation2016; @FritzGeoWikionlineplatform2012], which provide convenient and highly scalable tools for training data collection. Visually interpreted training labels present two particular problems. The first is that such labels have inevitable interpretation errors that can vary substantially according to the skill of the interpreter [@Estesplatformcrowdsourcingcreation2016; @WaldnerConflationexpertcrowd2019]. These errors are typically not accounted for in reported accuracy metrics (cite Arthur's paper), thus the degree to which such labelling error impacts map accuracy is unclear. However, studies of how land cover map error propagates through subsequent analyses [@Esteslargeareaspatiallycontinuous2018] suggests training data quality could have a large impact. The second problem is that visual interpretation depends on high resolution imagery (<5 m), as lower resolutions make it difficult for a human analyst to discern cropland. Typically the only practical source for such imagery are "virtual globe" basemaps provided by Microsoft and Google, which are composed of mosaics of various high resolution satellite and aerial image sources that typically span 3-5 years of time within a single country [@LesivCharacterizingspatialtemporal2018]. This within-mosaic temporal variation can set up a temporal mismatch between the imagery being interpreted and the imagery being classified, which are usually from a different source (e.g. Landsat, Sentinel) and selected to represent a single epoch. If a land change occurs in the interval between the two image sets (e.g. a new field was created), this can introduce error into the training data that is then passed on to the classifier. This source of error may be elevated in smallholder-dominated systems, where swidden systems are more comment (cite), or in rapidly developing agricultural frontiers.

We describe here a cropland mapping system that seeks to leverage the recent advances that help increase mapping accuracy over smallholder systems, while minimizing those newer sources of error that are associated with these advances.
